\documentclass[abstract=on,12pt]{scrreprt}

% Set packages to be used
\usepackage[hidelinks]{hyperref}	% Adds support for hyperlinks
\usepackage[british]{babel}			% Set the language to UK English
\usepackage[a4paper]{geometry}		% Set the paper type
\usepackage[T1]{fontenc}			% Change the encoding to allow for more character types
\usepackage{booktabs}				% More professional looking table layouts
\usepackage{graphicx} 				% For loading graphic files
\usepackage{multicol}				% Used to set column counts
\usepackage{ragged2e}				% for '\RaggedRight' macro (allows hyphenation)
\usepackage{setspace}				% Sets the spacing between lines
\usepackage{tabularx}				% for 'tabularx' environment and 'X' column type
\usepackage{titlesec}				% Allows custom formatting for sections
\usepackage{apalike}				% Format references in APA styling
\usepackage{gensymb}				% Allow inclusion of special characters, such as degrees
\usepackage{lmodern} 				% Type1-font for non-english texts and characters

% Set document specific info
\title{Is Immersion Possible in Non-Euclidean Virtual Environments?}
\subtitle{Outline Report and Summary of Progress}
\author{Nathan Boxhall-Burnett}
\setlength{\columnsep}{1cm}			% Set the spacing between columns
\onehalfspacing						% Set the spacing between the lines of text

% Set formatting for chapter titles
\titleformat{\chapter}[hang]{\huge\bfseries}{\thechapter}{1em}{\huge}

% Set formatting for section titles
\titleformat{\section}[hang]{\large\bfseries}{\thesection}{1em}{\large}

% Set formatting for section titles
\titleformat{\subsection}[hang]{\normalsize\bfseries}{\thesubsection}{1em}{\normalsize}

% Begin the document
\begin{document}

	% Title Page
	\maketitle

	% Remove page numbers
	\renewcommand\thepage{}

	% Abstract
	\begin{abstract}
		This Document is split into two parts.
		The first part is an outline of the contents of the report, with a table of contents at the beginning, followed by each individual section containing a description of what it will contain.

		The second part, starting on page \pageref{summary}, is a summary of progress for each section, which will give a brief outline of the progress that has been made for it so far.

		For the report itself, this section will contain a brief description of the project as a whole, as well as any benefits it has to the subject areas existing literature.

%		With Virtual Reality (VR) development and availability increasing as rapidly as it has in recent years, especially in the video game market, experiences that are capable from Virtual Environments (VE) that are not limited to the restrictions of the real world, and the effectiveness they have in a users perception, need to be considered.
%		This review explores the existing literature that covers the various requirements for creating a VE that consumers would perceive as 'realistic' in VR. As well as this, it also covers how these requirements have been, and can, be adapted to work inside of a world which does not follow the restrictions of real world geometry, such as in non-Euclidean or Escheresque space.
%		Gaps in the current literature are outlined, alongside perspective areas for future research.
	\end{abstract}

	% Document Acknowledgements
	\section*{Acknowledgements}
		Here is where I will thank my supervisor/examiner/caffeine for helping me along the way

	% Table of contents
	\tableofcontents

	% Reset the page count and add page numbering again
	\newpage
	\renewcommand\thepage{\arabic{page}}
	\pagenumbering{arabic}

	% Introduction
	\input{intro}

	% Literature Review
	\input{literature_review}
	% Maybe other background stuff too, who knows

	% Models/Product Design stuff
	\input{design}

	% Experiment
	\input{experiment}

	% Evaluation
	\input{evaluation}

	% Bibliography
	\nocite{*}	% Make all entries in the bibliography file appear in the references section, even if not cited directly
	\begingroup
		\chapter{References}
		\label{ref}
		This section will contain the list of resources that have either been directly referenced in the report, or have otherwise assisted in the creation of either the report or the product. Below is the list of references used as of \today.

		\begin{center}
			$\ast$~$\ast$~$\ast$
		\end{center}

		\renewcommand{\chapter}[2]{}		% Change chapter behaviour to make it not force the bibliography onto the following page
		\bibliographystyle{apalike}			% Set the bibliography to use APA formatting
		\bibliography{FinalYearProject}	    % Select the file to use for the bibliography
	\endgroup

	% Appendices
	\input{appendix}

	\chapter*{Summary of Progress}
	\label{summary}
	
		\section*{Current Progress}
			Here I will be covering the current progress that I have made in each of the sections previously discussed:
	
			\textbf{Abstract} - Work in progress, will be continuously updated as the work on the report continues, and will probably be one of the last things that is finalised.
	
	
			\textbf{Acknowledgements} - Finished.
			
	
			\textbf{1 - Introduction} - Work in progress, will be continuously updated as the work on the report and product continues.
			
	
			\textbf{2 - Literature Review}:
			
			\textbf{2.1} - Mostly complete, will probably require some tinkering once the rest of the lit review is finished.
			
			\textbf{2.2.1} - Mostly complete, could do with some rewording in places.
			
			\textbf{2.2.2} - Mostly complete, could do with some rewording in places.
			
			\textbf{2.2.3} - Mostly complete, could do with some rewording in places.
			
			\textbf{2.2.4} - Work in progress, could do with expanding.
			
			\textbf{2.3.1} - Mostly complete, could do with some rewording in places.
			
			\textbf{2.3.2} - Work in progress, could do with expanding.
			
			\textbf{2.3.3} - Work in progress, could do with expanding.
			
			\textbf{2.4.1} - Mostly complete, could do with some rewording in places.
			
			\textbf{2.4.2} - Mostly complete, could do with some rewording in places.
			
			\textbf{2.4.3} - Work in progress, could do with expanding.
			
			\textbf{2.4.4} - Work in progress, could do with expanding.
			
			\textbf{2.5} - Work in progress, will be expanded upon once the rest of the previous sections are completed.
			
	
			\textbf{3 - Design and Implementation}:
			
			\textbf{3.1} - Work in progress, could do with expanding.
			
			\textbf{3.2} - Work in progress, being expanded upon as tools are being used, and potentially changed.
			
			\textbf{3.3} - Work in progress, but not written up.
			
			\textbf{3.4} - Work in progress, but not written up.
			
	
			\textbf{4 - Experiment}:
			
			\textbf{4.1} - Not started yet, to be filled once the experiment has been started or having taken place.
			
			\textbf{4.2.1} - Not started yet, to be filled once the experiment has been started or having taken place.
			
			\textbf{4.2.2} - Not started yet, to be filled once the experiment has been started or having taken place.
			
			\textbf{4.2.3} - Not started yet, to be filled once the experiment has been started or having taken place.
			
			\textbf{4.2.4} - Not started yet, to be filled once the experiment has been started or having taken place.
			
			\textbf{4.3} - Not started yet, to be filled once the experiment has been started or having taken place.
			
	
			\textbf{5 - Evaluation}:
			
			\textbf{5.1} - Not started yet, will start this once the experiment has taken place and I have analysed the results.
			
	
			\textbf{6 - References} - This section is automated, so it will always be up to date.
			
	 
			\textbf{7 - Appendix}:
			
			\textbf{7.1} - Finished, just need to get the document signed and scanned.
			
			\textbf{7.2} - Work in progress, will be added to the report document once the experiments have taken place.
			
			\textbf{7.3} - Not started yet, to be filled once the report itself is completed.
		
		\section*{Notes}
			In general, I feel that so far I have not put as much effort into the project compared to my other modules. However, progress is still being made, and the write-up of these documents has definitely refocused me to work on the project to catch up to my initial timeline.
		

% End the document
\end{document}
